---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## What's going on with this data?

You need to change the contents of this Rmd! Replace the R code and markdown give below in this template document.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQBxdyDyrVLI6rj2PqUlKvn6RkQ3vvoTPhoH9w48pr1eQx6W26kxSYEagDe8cBONxiMRQ329dN1_jUZ/pub?gid=480293547&single=true&output=csv")

latest_data <- logged_data |>
  rename(
    platform  = "Which platform did you see the ad on?",
    category  = "Which category best describes the ad?",
    duration  = "How long was the ad (in seconds)?",
    skippable = "Was the ad skippable?",
    relevance = "How relevant was the ad to you?"
  )

avg_duration <- round(mean(latest_data$duration), 1)
avg_relevance <- round(mean(latest_data$relevance), 1)
total_obs <- nrow(latest_data)
```
```{css}
body {
  font-family: Arial, sans-serif;
  color: #333;
}
h2 {
  color: #2c5f8a;
}
p {
  font-size: 16px;
  line-height: 1.6;
}
```

## Observing Social Media Ads: What's Targeting Me?

Over the past week, I logged **`r total_obs` social media ad observations** across platforms including TikTok, Instagram, and YouTube. For each ad I recorded the platform, category, duration, whether it was skippable, and how relevant it felt to my interests.

The data shows that the average ad lasted **`r avg_duration` seconds**, and the average relevance score was **`r avg_relevance` out of 5**, suggesting that `r if(avg_relevance >= 3) "ads were generally well-targeted to my interests" else "ads were not particularly relevant to my interests"`.
```{r}
print(
  latest_data |>
    ggplot(aes(x = platform)) +
    geom_bar(fill = "steelblue") +
    labs(
      title = "Number of Ads Observed per Platform",
      x = "Platform",
      y = "Number of Ads"
    )
)
```

The chart above shows which platforms served the most ads during my observation period.
```{r}
print(
  latest_data |>
    ggplot(aes(x = category)) +
    geom_bar(fill = "coral") +
    labs(
      title = "Types of Ad Categories Observed",
      x = "Ad Category",
      y = "Number of Ads"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
)
```

The chart above breaks down the types of products and services being advertised to me. With an average relevance score of `r avg_relevance`/5 and average ad duration of `r avg_duration` seconds, this data gives a snapshot of how social media platforms are targeting my feed.

```
